---
title: "Tidy Modeling with R"
author: "Luca Hüsler"
date: "2022-10-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidymodels)
library(mlbench)
```

# 1 Software for modeling

https://www.tmwr.org/software-modeling.html#software-modeling

# 2 A Tidyverse Primer

```{r}
mtcars %>%
  select(ends_with("t"))
```

# 3 A Review of R Modeling Fundamentalsels



We are working with the `BostonHousing` dataset from the `mlbench` package

```{r}
boston_housing <- as_tibble(BostonHousing)
dim(boston_housing)
```

## Prepare train and test data

```{r}
boston_housing_split <- initial_split(boston_housing, prop = 0.75, strata = NULL)

boston_training <- boston_housing_split %>%
  training()

boston_test <- boston_housing_split %>%
  testing()
```



## Linear regression with tidymodels

We create models with the `parsnip` package. First, we define the model:

```{r}
lm_model <- linear_reg() %>%
  set_engine("lm") %>%
  set_mode("regression")
```


Now, we can fit the model with our training data:

```{r}
lm_fit <- fit(lm_model,
                  formula =  medv ~ ., 
                  data = boston_training)
lm_fit
```

Let's now do a prediction on the test data:

```{r}
boston_pred <- lm_fit %>% 
  predict(new_data = boston_test)

boston_pred
```

Finally, lets bind the predictions together with the test dataset:
```{r}
lm_test_results <- boston_test %>%
  bind_cols(boston_pred)
```


## Evaluating model performance

The `yardstick` package offers tools for evaluating model performance. All yardstick functions **require a tibble as input**, containing a column with the true outcome and one with the prediction.

### Calculation RMSE and R-Squared

```{r}
# root mean square error
lm_test_results %>% 
  rmse(truth = medv, estimate = .pred) 

# R-Squared
lm_test_results %>%
  rsq(truth = medv, estimate = .pred)
  
```

### R-Squared plots

```{r}
ggplot(lm_test_results, aes(x= medv, y = .pred)) +
  geom_point(alpha = 0.5) + 
  geom_abline(color = 'blue', linetype = 2) +
  coord_obs_pred() +
  labs(x = 'Actual Home Selling Price', y = 'Predicted Selling Price')
```

